### 2018-06-20 README.Rmd
fix class imports; update readme

---
output:
  rmarkdown::github_document
bibliography: "`r here::here('README-refs.bib')`"
---

@@

For standard use, install from
[Bioconductor](https://bioconductor.org/packages/methyvim):

```{r bioc-installation, eval = FALSE}
source("https://bioconductor.org/biocLite.R")
biocLite("methyvim")
```

>>>>

---
output:
  rmarkdown::github_document
bibliography: "README-refs.bib"
---

@@

For standard use, install from
[Bioconductor](https://bioconductor.org/packages/methyvim) using
[`BiocManager`](https://CRAN.R-project.org/package=BiocManager):

```{r bioc-installation, eval = FALSE}
if (!("BiocManager" %in% installed.packages())) {
  install.packages("BiocManager")
}
BiocManager::install("methyvim")
```
